### 2015-02-13 ms/ms.Rmd
address in italics

```{r,results="asis",echo=FALSE, message=FALSE}
writeLines(paste0(author_info$authors$name,
                        "^", author_info$authors$address_code, "^",
                        collapse = ", "))
writeLines("\n\n")
writeLines(paste0("^", author_info$address_table$code, "^ ",
                  author_info$address_table$address,"  "))
```

>>>>

```{r,results="asis",echo=FALSE, message=FALSE}
writeLines(paste0(author_info$authors$name,
                        "^", author_info$authors$address_code, "^",
                        collapse = ", "))
writeLines("\n\n")
writeLines(paste0("^", author_info$address_table$code, "^ *",
                  author_info$address_table$address,"*  "))
```
